2H qSIP Calculations

### 2021-11-09 qSIP_calculations.Rmd
filtered long chain fatty acids out of weighted mean calculations

```{r}
peaks_mapped_summarized <- peaks_mapped_with_zeros_analytes %>% 
  group_by(terrain, inc_time_d, compound) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE)
```

@@

weighted_time_course <- peaks_mapped_summarized %>% 
  group_by(terrain, inc_time_d) %>%
  summarize(at2H_weighted = sum(at2H * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))

@@

```{r}
gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )
```

@@

gen_calc_data_summarized <- peaks_mapped_summarized %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time (d)
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )

weighted_turnover_summarized <- gen_calc_data_summarized %>% 
  group_by(terrain, inc_time_d) %>%
  summarize(u_d_weighted = sum(u_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))

>>>>

```{r}
peaks_mapped_summarized <- peaks_mapped_with_zeros_analytes %>% 
  group_by(terrain, inc_time_d, compound) %>% 
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE)
```

@@

weighted_time_course <- peaks_mapped_summarized %>% 
  group_by(terrain, inc_time_d) %>%
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  summarize(at2H_weighted = sum(at2H * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))

@@

```{r}
gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )
```

@@

gen_calc_data_summarized <- peaks_mapped_summarized %>% 
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time (d)
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )

weighted_turnover_summarized <- gen_calc_data_summarized %>% 
  group_by(terrain, inc_time_d) %>%
  summarize(u_d_weighted = sum(u_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE),
            gen_d_weighted = sum(gen_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))
